Meta-analysis

### 2019-11-06 05_MetaAnalysis.Rmd
updated LME models to include spray managment without early_plus or late_plus

```{r}

@@

>>>>

m4 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat)

m5 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (factor(spray_management) | trial_ref), data = slim_PM_dat) # Model failed to converge

m5.0 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + (1 | trial_ref), data = slim_PM_dat) # Model failed to converge

anova(m4,m5) # m5 has a much lower AIC and significantly better model

anova(m5,m5.0)

summary(m5.0)

@@

```{r LME_cluster_disease_mod}
m6 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) * PM_final_severity +
              (factor(spray_management) | trial_ref), 
           data = slim_PM_dat)

m7 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) * PM_final_severity + 
              (factor(spray_management) | trial_ref), 
           data = slim_PM_dat)

anova(m5,m6) # 65 has a lower AIC but not evaluated as a significantly better model

summary(m6)

```{r LME_slimer_cluster_disease_mod}
slimer_PM_dat <- read.csv("data/slimer_PM_clusterdat.csv")

m8 <- lmer(grain_yield.t.ha*1000 ~ factor(spray_management) +
              (factor(spray_management) | trial_ref), 
           data = slimer_PM_dat)

m9 <- lmer(log(grain_yield.t.ha*1000) ~ factor(spray_management) + 
              (factor(spray_management) | trial_ref), 
           data = slimer_PM_dat)

anova(m8,m9) # 65 has a lower AIC but not evaluated as a significantly better model

summary(m9)
